Race to the Ballot Box: Will Demographics Decide a Winner This Year?

### 2024-11-01 paper/paper.qmd
Updating figures in the paper

```{r, fig.width = 8, fig.height=6, echo = FALSE, message = FALSE}
predicted_data |>
  filter(swing_state == 1, candidate_trump == 1) |>
  select(state, end_date, predicted_pct_trump) |>
  group_by(state, end_date) |>
  summarise(mean = mean(predicted_pct_trump), .groups = "drop") |>
  ggplot(aes(x = end_date, y = mean)) +
  geom_point(size = 0.5) +
  scale_y_continuous(limits = c(0, 100)) +
  geom_smooth(se = FALSE, color = "red2", method = "loess", formula = 'y ~ x') +
  facet_wrap(vars(state)) +
  labs(x = NULL, y = NULL)
```

@@

# Create the overlay plot
overlay_plot <- ggplot(combined_data_long, aes(x = end_date, y = mean, color = candidate)) +
  geom_point(size = 0.5) +
  geom_smooth(se = FALSE, method = "loess", formula = 'y ~ x') +
  scale_y_continuous(limits = c(0, 100)) +
  labs(x = NULL, y = NULL, color = "Candidate") +
  scale_color_manual(values = c("mean_trump" = "red2", "mean_harris" = "blue2")) +
  theme(legend.position = "top")

@@

>>>>

```{r, fig.width = 8, fig.height=6, echo = FALSE, message = FALSE}
predicted_data |>
  filter(swing_state == 1, candidate_trump == 1) |>
  select(state, end_date, predicted_pct_trump) |>
  group_by(state, end_date) |>
  summarise(mean = mean(predicted_pct_trump), .groups = "drop") |>
  ggplot(aes(x = end_date, y = mean)) +
  geom_point(size = 0.5) +
  scale_y_continuous(limits = c(0, 100)) +
  geom_smooth(se = FALSE, color = "#d92b34", method = "loess", formula = 'y ~ x') +
  facet_wrap(vars(state)) +
  labs(x = NULL, y = NULL)
```

@@

# Create the overlay plot
overlay_plot <- ggplot(combined_data_long, aes(x = end_date, y = mean, color = candidate)) +
  geom_point(size = 0.5) +
  geom_smooth(se = FALSE, method = "loess", formula = 'y ~ x') +
  scale_y_continuous(limits = c(0, 100)) +
  labs(x = NULL, y = NULL, color = "Candidate") +
  scale_color_manual(values = c("mean_trump" = "#d92b34", "mean_harris" = "#2635bd")) +
  theme(legend.position = "top")

@@

```{r, echo = FALSE, fig.height=6, fig.width=8, warning = FALSE}
library(usmap)

sample <- predicted_data_harris |> 
  merge(predicted_data_trump, all = T) |>
  left_join(electoral_votes, by = c("state" = "state")) |>
  mutate(predicted_winner = ifelse(replace_na(predicted_pct_harris, 50) <
                                     replace_na(predicted_pct_trump, 50), 
                                   "Trump", "Harris"))

plot_usmap(regions = "state", data = sample, 
           values = "predicted_winner") +
  scale_fill_manual(values = c("#2635bd", "#d92b34", "grey90")) +
  theme(legend.position = "top")
```
